---
title: "Data 605 Week 5"
author: "Tyler Baker"
date: "2/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stats)
```

# 1
Bayes' Theroem
P(A|B) = P(B|A)P(A)/P(B)

## Part a

P(disease|positive) = (P(positive|disease)P(disease))/(P(positive|disease)P(disease) + P(positive|non-disease)P(non-disease))
```{r}
sensitivity = .96
# sensitivy = P(positive|disease)
specific = .98
false_positive = 1-specific
#false_positive = P(positive|non-disease)
prevelence = .001
# prevelence = P(disease)
disease_free = 1 - prevelence
# disease_free = P(non-disease)

solution = (sensitivity * prevelence)/((sensitivity * prevelence)+(false_positive * disease_free))

print(solution)
```

## Part b

I'm not sure where to even start. I don't know what 'per positive case total' means, nor do I know what exactly is meant by 'per administration'.

# 2

Binomail
b(n,p,j) = (n choose j)(p^j)((1-p)^(n-j)

## part a

What is the probability that after 24 months you received exactly 2 inspections
```{r}
n = 24
j = 2
p = .05
sol_two_a = (choose(n,j))*(p^j)*((1-p)^(n-j))
print(sol_two_a)
```

## part b

Goal: find 1 - b(24, .05, 1) - b(24, 0.05, 0)
```{r}
one_visit <- (choose(24,1))*(p)*((1-p)^23)
no_visit <- (choose(24,0))*((1-p)^24)
sol_two_b <- 1 - one_visit - no_visit
print(sol_two_b)
```

## part c

```{r}
sol_two_c <- 1 - sol_two_b
print(sol_two_c)
```

## part d

EV = sum(P(x_i) * x_i)

```{r}
range <- c(0:24)
values<- c()
for (i in range){
  x<- (choose(24,i))*(p^i)*((1-p)^(24-i))
  values <- append(values, x)
}
ev <- sum(values * range)
```

## part e

```{r}
sd <- sum(values * (range - ev)^2)
```

# 3
Poisson
p(x, l) = (e^(-l)l^(x))/x!

l = average number of events given a time interval

## part a
```{r}
l <- 10
x <- 3
print((exp(1)^(-l)*l^(x))/factorial(x))
```

## part b

find 1 - probability of less than 10 people showing up per hour.
```{r}
range <- c(0:10)
values <- c()
for (i in range){
  x <- (exp(1)^(-l)*l^(i))/factorial(i)
  values <- append(values, x)
}
print(1 - sum(values))
```

## part c

I would expect 80 people to arrive in 8 hours.

## part d

```{r}
print(sqrt(10))
```

## part e

I'm not sure what the question means. 

# 4
Hypergeometric

h(n,a,k) = ((choose(k,x))*(choose((n-k), (a-x))))/(choose(n,a))

n = sample size
a = number of picks(without replacement)
k = successes
a - k = failures
x = selecting correctly

## part a

```{r}
n = 30
k = 15
a = 6
x = 5

print(((choose(k,x))*(choose((n-k), (a-x))))/(choose(n,a)))
```

## part b

I would have expected my subordinate to send 3 nurses and 3 non-nurses.

# 5
Geometric
P(X=x) = ((1-p)^(x-1))*p

## part a
```{r}
p <- .001
x <- 1200
print(((1-p)^(x-1))*p)
```

## part b
```{r}
x <- 1500
print(((1-p)^(x-1))*p)
```

## part c

```{r}
mean <- 1/p
print(mean)
```

## part d

P(B|A) = P(A and B)/ P(A)
P(B|A) = P(A|B)P(B)/P(A)

```{r}
p_of_a <- ((1-p)^(1200-1))*p
p_of_b <- ((1-p)^(100-1))*p
p_of_a_inter_p_of_b<- p_of_b - p_of_a
p_of_a_given_b <- p_of_a_inter_p_of_b/ p_of_b

print((p_of_a_given_b * p_of_b)/p_of_a)
```

This isn't correct. I know that I can't have a probability larger than 1.

# 6
Because the question is dealing with time intervals we should use the Poisson distribution.

(exp(1)^(-l)*l^(x))/factorial(x)

## part a
```{r}
l <- 1

# solution will be to find the values when x =0, 1, 2. Then subtract the values from 1.

range <- c(0:2)
values <- c()
for (i in range){
  x <- (exp(1)^(-l)*l^(i))/factorial(i)
  values <- append(values, x)
}
print(1 - sum(values))
```

## part b

The expected value is the mean which is about 1 as stated in the problem.

# 7

## part a

Since, the distribution is uniformly distributed we know that that means are function is flat from 0 minutes to 30 minutes. Thus, we know that there is a 2/3 chance that the patient will wait more than 10 minutes.

## part b

I think we can make this question a lot easier by simply rephrasing the question. Instead we can simply think of the probability that the patient waits for longer than 15 minutes. This is 1/2.

## part c 

The mean is 15 minutes.

# 8
Exponential distribution
m = 1 / mu
pdf = m*(exp(1)^(-mx))

## part a

exepcted failure time = 10 years

## part b

standard deviation = 10 years

## part c
```{r}
m = .1
x = 8
print(m*(exp(1)^((-m)*x)))
```

## part d
```{r}
m = .1
x = 8
integrand <- function(x) {m*(exp(1)^((-m)*x))}
integrate(integrand, lower = 8, upper = 10)
```

